\noindent In~\cref{tab:T41} the event yields after the preselection are displayed for different numbers of $b$-tagged jets. For the integrated luminosity in data, the total number of events for one or two $b$-tagged jets are shown, as well as the corresponding signal and background contributions. Furthermore, the data-simulation comparison is given. In addition, the event yields for events with at least one $b$-tagged jet is given. All shown results, just include statistical uncertainties.\\

\noindent As mentioned above, the main background sources are indeed the $W$ + jets events followed by QCD-multijet background, while rest, e.g. diboson  and $Z$ + jet events, play a minor role. \\
\noindent On can clearly see that the requirement of exactly two $b$-tagged jets, decreases the total number of events dramatically. However, more important is the fact that especially the major background sources,$W$-jets and QCD-multijet events, can be reduced by one order of magnitude, while the data-simulation ratio remains in the same range as for one $b$-tagged samples.\\
\noindent This impressive results, which are in good agreement with the observations of the previous measurement, show that the background can be noticeable reduced by applying the two $b$-tagged cut. Thus, samples with four jets, of which two have to be $b$-tagged jets, are used for the further analysis. This is exactly the same choice as for the previous measurements.\\
\noindent Furthermore, if one compares the different background fractions with the yields from the 7 and 8~TeV measurement, one can see that there are deviations. This can be explained by the fact that the cross-sections of the different background source  increase different with the center-of-mass energy.\\ 